%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hieu Do - Resume
% 7/26/2016
%
% Reference:
% Debarghya Das (http://debarghyadas.com)

\documentclass[]{hieudo-build}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Li-Pin Juan}
{\urlstyle{same}
	\faEnvelope \href{mailto:libinruan@umn.edu}{ libinruan@umn.edu}\\
	\faGithub \href{https://github.com/libinruan}{   GitHub://libinruan}\\
	\faLinkedinSquare \href{https://www.linkedin.com/in/libinruan}{ LinkedIn://libinruan} \\
    \faHome \href{https://libinruan.com}{ www.libinruan.com}
}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.34\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{University of Minnesota}
\descript{Twin Cities, MN}
Ph.D. in Applied Economics \\
Expected Grad. May 2018 \\
Cum. GPA: 3.6/4.0\\
\sectionsep
\subsection{Georgia Institute of Technology}
\descript{Atlanta, GA}
M.Sc. in Statistics \\
Grad. Aug 2008. GPA: 3.8/4.0
Recipient of Taiwan Merit Scholarship, awarded by Ministry of Education, R.O.C. Taiwan
\sectionsep
\subsection{National Taiwan University}
\descript{Taipei, Taiwan}
M.B.A. in Financial Engineering \\
Grad. May 2000. GPA: 3.9/4.0

\section{Coursework}
\subsection{University of Minnesota}
Econometric Analysis \\
Dynamic Programming \\
\sectionsep
\subsection{Georgia Institute of Technology}
Computational Data Analysis \\
(Machine Learning) \\
Computational Statistics \\
Time Series Analysis \\
Nonparametric Data Analysis \\
Multivariate Data Analysis \\
Linear Statistical Model \\
%\subsection{Theoretical}
%Asset Pricing \\
%Micro- \& Macro-economics
Nonlinear Optimization \\
Statistical Estimation \\
Hypothesis Testing 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\subsection{Computer}
\location{Proficient in}
Python, R, MATLAB, Fortran \\ 
\location{Knowledge of}
SQL, C++, Visual Basic \\
%\subsection{Technical}
\location{Familiar with}
Linux, Git, Visual Studio, \LaTeX, Microsoft Office \\
%Adobe Illustrator \& InDesign \\ 
\sectionsep

% \sectionsep
% \subsection{Languages}
% \location{Native fluency:} English, Vietnamese\\
%\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     HACKATHONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Hackathons}
% HackMIT \textbullet{} hackNY \\
% WearHacks NY \textbullet{} Hackademics VN \\
% \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Coursework}
%\subsection{Graduate}
%Econometric Analysis \\
%Computational Economics \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ADDITIONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Activities}
%NYU Tandon Honors Program\\
%Tech@NYU - Freshman Circuit \\
%The Westminster News \\
%\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% Dean's List\\
% NYU PROMISE Scholarship\\
% Shelby C. Davis Scholarship\\
% President’s Circle Scholarship\\
% \sectionsep

%\sectionsep
%\DTMsetdatestyle{mylastupdate}
%\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}

\workplace{Federal Reserve Bank of Minneapolis}{Jul 2014 – Jun 2017}\\
\position{Research Analyst}{Minneapolis, MN}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Provided analytical support for senior management and managed a process to produce a set of briefing materials on current economic conditions for the bank’s Board of Directors and the bank president to give Minneapolis Fed leadership a succinct picture of national and regional economic conditions. 
%\item Building a database management system to monitor all NYU data centers worldwide using SQL and Oracle APEX.
%\item Updating an internal server request tool by improving its user-interface and the service request process.
\item Skills: Data piping (from Haver Analytics etc.), Data cleaning, Data visualization, Excel automation with Visual Basic.
\end{tightemize}
\sectionsep

\workplace{University of Minnesota}{Aug 2012} \\
\position{Instructor in Numerical Analysis with MATLAB}{St. Paul, MN}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Taught a 5-day short course for incoming PhD students in Applied Economics to help them acquire basic programming skill to implement quantitative methods in core courses like Econometrics and Macroeconomics.

%\item Researched distributed monitoring solutions for the Seattle Testbed, a distributed cloud platform, using Python and an in-house restricted version of Python (Repy).
%\item Designed the monitoring pipeline that accounts for the monitoring tools' accessibility, modularity, and scalability.
\end{tightemize}
\sectionsep

\workplace{Institute of Statistical Science, Academia Sinica}{Jul 2005 – Aug 2006} \\
\position{Research Assistant}{Taipei, R.O.C. Taiwan}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built an automated technical analysis algorithm on capturing stock market anomalies.
\item Implemented statistical analysis on data from the Thomson Reuters Lipper Hedge Fund performance database to investigate the differences in the risk-adjusted return between liquidated and alive hedge funds.
\item Skills: C++ and R programming, Text data cleaning, Random sampling.
\end{tightemize}
%\sectionsep

% \runsubsection{The Westminster News} \\
% \descript{Co-Editors-in-Chief (2014) | Layout Editor (2012) }
% \location{Sep 2012 – May 2015 | Simsbury, CT}
% \begin{tightemize}
% \item Led 30+ staff at a 400-student boarding school to publish the monthly school newspaper.
% \item Consulted in layout design and technology application.
% \end{tightemize}
% \sectionsep

% \runsubsection{VietAbroader Organization} \\
% \descript{Program Assistant Manager | VAPedia Associate }
% \location{Mar 2013 – Mar 2014 | Ho Chi Minh City, Vietnam}
% \begin{tightemize}
% \item VietAbroader is a non-profit organization run by Vietnamese students abroad.
% \item Designed the high school content for the VAPedia website.
% \item Assisted in recruiting guest speakers and volunteers for VietAbroader Study-Abroad Conference 2013.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Academic Project}
\runsubsection{Quantifying the Impact of Wealth-Based Taxation on Life-Cycle Patterns of US Household Wealth Holdings}
%\descript{}
\location{Ph.D. thesis project.}
\begin{tightemize}
%\item Statistically estimate the age profiles of US household asset holdings among worker and business households, establish a quantitative model to mimic the empirical findings and employ it as a workhorse for tax policy experiments.
\item Contributions: Statistically characterize US household asset holdings over the lifetime. Quantifying the effects of wealth taxes on the economy as opposed to capital income taxation.
\item Skills: Panel data analysis. Partially linear regression (semi-nonparametric statistical modeling). Stochastic dynamic general equilibrium modeling. Parallel computing.
\end{tightemize}
\sectionsep

\runsubsection{Poverty Trap, Financial Openness and Economic Growth}
\descript{24th Australasian Finance and Banking Conference Paper 2011}
%\location{Best Software, Wearhacks NY 2015}

%\sectionsep 

%\runsubsection{Sia}
%\descript{}
%\location{2nd Prize, Hackademics VN 2015}
%A pioneering sex-ed website that promotes sexuality and gender awareness among Vietnamese teenagers. Built with MEAN stack.
%\sectionsep

%\runsubsection{Imagely}
%\descript{}
%A web app that enhances language-learning experience by generating new words from pictures. Built with MEAN stack using Clarifai API and Yandex API.
%\sectionsep 

\section{Certificates}
\href{https://www.datacamp.com/statement-of-accomplishment/track/2380b142ca0efe8ccf46d72295e6c90ef2b7b165?lipi=urn%3Ali%3Apage%3Ad_flagship3_profile_view_base%3BC877CZzpQNG%2BcsyBdM5s%2Fw%3D%3D}{Python Programmer \#24624} \hfill \href{https://www.datacamp.com/home}{DataCamp}, Feb 2018 \\
\href{https://www.datacamp.com/statement-of-accomplishment/track/acd2c1fde62ac121f65f4e2f004ee9f5cdbd06ba?lipi=urn%3Ali%3Apage%3Ad_flagship3_profile_view_base%3BC877CZzpQNG%2BcsyBdM5s%2Fw%3D%3D}{Data Scientist with Python \#24854} \hfill \href{https://www.datacamp.com/home}{DataCamp}, Feb 2018 \\

\end{minipage} 

\end{document}  
